Cochain level May--Steenrod operations

### 2021-07-30 main.tex
Split-off abstract and update address and email

\author[R. Kaufmann]{Ralph M.\ Kaufmann}
\address{Department of Mathematics, Department of Physics and Astronomy, Purdue University}
\email{rkaufman@purdue.edu}

\author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
\address{Laboratory for Topology and Neuroscience, EPFL \and
Department of Mathematics, University of Notre Dame}
\email{amedinam@nd.edu}
\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Max Plank Institute for Mathematics where part of this work developed.}

\subjclass[2010]{55S05, 55U05, 55S10, 55S12; 55-04, 55U15, 55S15}
\keywords{Steenrod operations, Dyer--Lashof operations, operads, simplicial cochains, cubical cochains}

\begin{abstract}
	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander--Whitney's chain approximation to the diagonal. He later defined his homonymous operations for all primes using the homology of symmetric groups. This approach enhanced the conceptual understanding of the operations and allowed for many advances, but lacked the concreteness of their definition at the even prime. In recent years, thanks to the development of new applications of cohomology, having definitions of Steenrod operations that can be effectively computed in specific examples has become a key issue. This article provides such definitions at all primes using the operadic viewpoint of May, and defines multioperations that generalize the cup-$i$ products of Steenrod on the simplicial and cubical cochains of spaces.
\end{abstract}

@@

\tableofcontents
\input{introduction}
\input{preliminaries}
\input{groups}
\input{operads}
\input{steenrod}
\input{effective}
\input{outlook}
\bibliography{bibliography}

>>>>

\author[R. Kaufmann]{Ralph M.\ Kaufmann}
\address{R. Kaufmann, Department of Mathematics, Department of Physics and Astronomy, Purdue University}
\email{rkaufman@purdue.edu}

\author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
\address{A. Medina-Mardones, Max Planck Institute for Mathematics \and
University of Notre Dame du Lac}
\email{ammedmar@mpim-bonn.mpg.de}
\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Laboratory for Topology and Neuroscience at EPFL.}

\subjclass[2010]{55S05, 55U05, 55S10, 55S12; 55-04, 55U15, 55S15}

\keywords{Steenrod operations, Dyer--Lashof operations, operads, simplicial cochains, cubical cochains}

\input{abstract}

@@

\setcounter{tocdepth}{1}
\tableofcontents

\input{introduction}
\input{preliminaries}
\input{groups}
\input{operads}
\input{steenrod}
\input{effective}
\input{outlook}

\bibliography{bibliography}
